The Influence of Radial Drift and Gas Accretion on the C/O Ratio in Protoplanetary Disks

### 2016-04-14 Dissertate-Harvard-LaTeX/chapters/introduction.tex
upd

\begin{figure}[t!]
\centering
\includegraphics[width=0.8\textwidth]{figures/proto.pdf}
%\vspace{-0.5in}
\caption{The standard picture of molecular cloud to protostar to protoplanetary disk to planet formation. Reprinted by permission from Karin \"Oberg.}
\label{fig:proto}
\end{figure}

%\subsection{Disk Temperature and Density Structure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.8\textwidth]{figures/CO.png}
%\vspace{-0.5in}
\caption{ALMA detection of the CO snowline in TW Hya at 30 AU. Reprinted by permission from Karin \"Oberg.}
\label{fig:qi13}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.8\textwidth]{figures/oberg11.png}
%\vspace{-0.5in}
\caption{The C/O ratio in gas (solid line) and dust (dashed line) as a function of semimajor axis in a static disk. The dotted line shows the stellar value of 0.54. Gas-phase C/O ratios of order unity can be achieved in the outer disk. Reprinted by permission from Karin \"Oberg. }
\label{fig:oberg}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{figures/proto.pdf}
%\vspace{-0.5in}
\caption{The standard picture of molecular cloud to protostar to protoplanetary disk to planet formation. Reprinted by permission from Karin \"Oberg.}
\label{fig:proto}
\end{figure}

%\subsection{Disk Temperature and Density Structure}
\subsection{Disk Temperature and Density Structure}

The midplane temperature in a protoplanetary disk is set both by the irradiation from the host star and by accretion heating (e.g., \citealt{armitage10}). Accretion heating dominates in the inner disk (typically within a few AU) where the accretion flows are strongest, while the outer disk is dominated by stellar irradiation. While the irradiation component of the temperature simply follows a power-law in radius, the accretional component is determined by viscosity and the gas mass accretion rate, which in turn depend on the temperature itself, as well as the gas surface density (for a more complete review see \citealt{shakura73}). As the gas surface density changes with time in an active disk, it follows that determining the midplane temperature in an active disk in which both stellar irradiation and accretion heating contribute to the thermal evolution of the disk is non-trivial. We simplify this problem in Chapters 4 and 5 by assuming a steady-state disk with a constant mass accretion flow, and by solving the thin disk Shakura-Sunyaev equations.

The gas surface density in a viscous disk follows the continuity equation, and is set by both the disk temperature and viscosity. Infall of material onto the disk or outflow may also contribute to the gas surface density evolution \citep{birnstiel10}. The dust surface density can be described by an advection-diffusion equation (e.g., \citealt{birnstiel12}), where both the radial movement of the dust and diffusion contribute to its evolution. The diffusion term is due to the fact that the dust is turbulently mixed by the gas, which causes a change in the dust-to-gas ratio and thus a radial gradient in the ratio between solid and gas surface densities. In the case of small particles that are well coupled to the gas, the surface density follows that of the gas and a constant dust-to-gas ratio is maintained. The movement of larger particles, however, is affected both by radial drift, gas drag and diffusion, which cause the dust surface density to "decouple" from that of the gas. This results in depletion of solids in some disk regions and a pile-up in others, depending on a particle's radial drift velocity and the level of turbulent mixing. The dust surface density is further affected by grain growth and fragmentation. We do not address all these effects in Chapter 4 and 5, and instead assume a constant inflow of particles such that the dust surface density remains spatially and temporally constant. We note, however, that these effects have to be taken into account for a more realistic modeling of the dust surface density, and thus of the surface density evolution of volatiles, both in solid and gaseous form.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{figures/CO.png}
%\vspace{-0.5in}
\caption{ALMA detection of the CO snowline in TW Hya at 30 AU. Reprinted by permission from Karin \"Oberg.}
\label{fig:qi13}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{figures/oberg11.png}
%\vspace{-0.5in}
\caption{The C/O ratio in gas (solid line) and dust (dashed line) as a function of semimajor axis in a static disk. The dotted line shows the stellar value of 0.54. Gas-phase C/O ratios of order unity can be achieved in the outer disk. Reprinted by permission from Karin \"Oberg. }
\label{fig:oberg}
\end{figure}
